---
title: "association rules"
author: "EZRA MAGETO"
date: "7/17/2021"
output: html_document
---

# ASSOCIATION RULES 

#### This section will require that you create association rules that will allow you to identify relationships between variables in the dataset. You are provided with a separate dataset that comprises groups of items that will be associated with others. Just like in the other sections, you will also be required to provide insights for your analysis.

# LOADING THE DATASET

```{r}
#loading the arules library
library(arules)
```

```{r}
#previewing the dataset
super<-read.transactions("http://bit.ly/SupermarketDatasetII",sep ="," )
head(super)
```

six transactions and 119 items present

```{r}
# Verifying the object's class
class(super)

```

```{r}
#previewing the first four transactions
inspect(super[1:4])
```

```{r}
#previewing the items that make the dataset
items<-as.data.frame(itemLabels(super))
colnames(items) <- "Item"
head(items,10)
```

```{r}
#summary of the transactions
summary(super)
```

```{r}
#Exploring the frequency of some articles 
# i.e. transacations ranging from 8 to 10 and performing 
# some operation in percentage terms of the total transactions 
# 
itemFrequency(super[, 8:10],type = "absolute")
round(itemFrequency(super[, 8:10],type = "relative")*100,2)
```

```{r}
#plotting the top 10 items
par(mfrow = c(1, 2))

# plot the frequency of items
itemFrequencyPlot(super, topN = 10,col="darkgreen")
itemFrequencyPlot(super, support = 0.1,col="darkred")
```

```{r}
# Building a model based on association rules of min support o.001 and confidence o.8

rules <- apriori(super, parameter = list(supp = 0.001, conf = 0.8))
rules
```

set of 74 rules are created with this parameter

```{r}
# Building a model based on association rules of min support o.002 and confidence 0.8

rules <- apriori(super, parameter = list(supp = 0.002, conf = 0.8))
rules
```

a set of two rules is created with this parameter

```{r}
# Building a model based on association rules of min support 0.001 and confidence 0.6

rules <- apriori(super, parameter = list(supp = 0.001, conf = 0.6))
rules
```

reducing the confidence increases the set of rules while increasing the min support reduces the set of rules

```{r}
#summary of the rules
summary(rules)
```

```{r}
# Observing rules built in our model i.e. first 5 model rules
# ---
# 
inspect(rules[1:5])
```

if one buys low fat yogurt and shallot they are 70% likely to buy cookies

```{r}
# sorting the rules in decreasing order of confidence
rules <- sort(rules, by = "confidence", decreasing = TRUE)
inspect(rules[1:5])
```

four rules have a confidence level of 100 while the remaining one has a confidence level of 95
