---
title: "ip-week-14-core"
author: "EZRA MAGETO"
date: "7/17/2021"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

# DEFINITION OF THE PROBLEM 

#### You are a Data analyst at Carrefour Kenya and are currently undertaking a project that will inform the marketing department on the most relevant marketing strategies that will result in the highest no. of sales (total price including tax) 

# METRICS OF SUCCESS 

#### Your project has been divided into four parts where you'll explore a recent marketing dataset by performing various unsupervised learning techniques and later providing recommendations based on your insights. 

# EXPERIMENTAL DESIGN 

#### 1.Perform dimensionality reduction using PCA

####  2.Perform feature selection using different methods

# LOADING THE DATASET

```{r}
carre<-read.csv("http://bit.ly/CarreFourDataset")
```

```{r}
#previewing the head of the dataset
head(carre)
```

```{r}
#previewing the tail of the dataset
tail(carre)
```

```{r}
#viewing the datatable
View(carre)
```

# EXPLORING THE DATASET

```{r}
#checking the shape of the dataset
dim(carre)
```

```{r}
#checking for the column names
colnames(carre)
```

```{r}
#checking internal structure of the dataset
str(carre)
```

# CLEANING THE DATASET

```{r}
#checking for the sum of missing values
colSums(is.na(carre))
```

there are no missing values in each column

```{r}
#checking for duplicates
anyDuplicated(carre)
```

there are no duplicates in the dataset

```{r}
#dropping the Invoice.ID,date and time
carre$Invoice.ID<-NULL
carre$Date<-NULL
carre$Time<-NULL
carre$gross.margin.percentage<-NULL
dim(carre)
```

the Invoice.ID,date,time and gross margin percentage column is not
necessary in the analysis

```{r}
#changing categorical columns to numeric

carre$Branch <- as.numeric(carre$Branch)
carre$Customer.type<-as.numeric(carre$Customer.type) 
carre$Gender <- as.numeric(carre$Gender)
carre$Product.line <- as.numeric(carre$Product.line)
carre$Payment <- as.numeric(carre$Payment)
```

```{r}
colnames(carre)
```

# DIMENSIONALITY REDUCTION 

## 1.0 PCA

```{r}
df <- carre[,c(5,6,7,9,10,11,12)]
head(df)
```

```{r}
carre.pca <- prcomp(carre[,c(5,6,7,9,10,11,12)], center = TRUE, scale. = TRUE)
summary(carre.pca)
```

PC1 forms 70% of the total variance while PC2 forms 14% of the total
variance.This carries most of the information in the dataset

```{r}
#Calling str() to have a look at your PCA object
str(carre.pca)
```

```{r}
# loading libraries to plot our PCA
Sys.setenv(R_REMOTES_NO_ERRORS_FROM_WARNINGS="true")



library(devtools)
library(usethis)


install_github("vqv/ggbiplot",force = TRUE)

2
```

```{r}
#visualizing the pca
library(ggbiplot)
ggbiplot(carre.pca)
```

```{r}
# adding more detail to the plot
ggbiplot(carre.pca, labels = rownames(carre), obs.scale = 1, var.scale = 1)
```

# 2.0 FEATURE SELECTION 

This section requires you to perform feature selection through the use
of the unsupervised learning methods learned earlier this week. You will
be required to perform your analysis and provide insights on the
features that contribute the most information to the dataset.

# 2.1 FILTER METHOD

```{r}
#getting the necessary libraries
library(caret)
library(corrplot)
library(lattice)
```

```{r}
# Calculating the correlation matrix
# ---
#
correlationMatrix <- cor(carre)
correlationMatrix
```

```{r}
# Find attributes that are highly correlated
# ---
#
highlyCorrelated <- findCorrelation(correlationMatrix, cutoff=0.75)

# Highly correlated attributes
# ---
# 
highlyCorrelated

names(carre[,highlyCorrelated])
```

```{r}
# Removing Redundant Features 
# ---
# 
carre2<-carre[-highlyCorrelated]
```

```{r}

#corrplot(cor(carre2), order = "hclust")
```

# 2.2 WRAPPER METHOD

```{r}
#required libraries
library(mclust)
library(clustvarsel)
```

```{r}
#carrying greedy search

greed = clustvarsel(carre, G = 1:8)
greed
```

```{r}

#building the clustering model
Subset1 = carre[, greed$subset]
mod = Mclust(Subset1, G = 1:8)
summary(mod)
```

```{r}
#visualising
plot(mod ,c("classification"))
```

# 2.3 EMBEDDED METHOD

```{r}
#required libraries
library(wskm)
library(cluster)
```

```{r}
# Cluster Plot against 1st 2 principal components
# ---
#
clusplot(carre[1:7], model$cluster, color=TRUE, shade=TRUE,
         labels=2, lines=1,main='Cluster Analysis for carre')
```

```{r}
#getting the weights
round(model$weights*100,2)
```

# RECOMMENDATION

LOADING...

couldn't come up with conclusion because of the chunks taking too long
to load
